---
title: "R Markdown Presentation & Plotly"
author: "Gabriela Ochoa"
date: "29 marzo 2021"
output: html_document
---

## Instructions
Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. 

## Review criteria

The rubric contains the following two questions:

1. Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?
2. Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?

## Code and Data

Through this code we try to plot the closing prices of major European stock indices in the years of 1991 to 1998.

**Daily Closing Prices of Major European Stock Indices, 1991-1998**

_Description_

Contains the daily closing prices of major European stock indices: Germany DAX (Ibis), Switzerland SMI, France CAC, and UK FTSE. The data are sampled in business time, i.e., weekends and holidays are omitted.

_Format_

A multivariate time series with `1860 observations` on `4 variables`. The object is of class `"mts"`.

_Source_

The data were kindly provided by Erste Bank AG, Vienna, Austria.

```{r, echo=TRUE, eval=FALSE}
library(plotly)
library(tidyr)
library(dplyr)
data("EuStockMarkets")
stocks <- as.data.frame(EuStockMarkets) %>%
  gather(index, price) %>%
  mutate(time = rep(time(EuStockMarkets), 4))
plot_ly(stocks, x = ~time, y = ~price, color = ~index, mode = "lines")
```

## Plot

```{r, echo=FALSE, eval=TRUE, message=FALSE}
library(plotly)
library(tidyr)
library(dplyr)
data("EuStockMarkets")
stocks <- as.data.frame(EuStockMarkets) %>%
  gather(index, price) %>%
  mutate(time = rep(time(EuStockMarkets), 4))
plot_ly(stocks, x = ~time, y = ~price, color = ~index, mode = "lines")
```