---
title: "Regression Models Course Project"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
  word_document: default
---

Supposing I work for _Motor Trend_, 
a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:  

- **"Is an automatic or manual transmission better for MPG"**
- **"Quantify the MPG difference between automatic and manual transmissions"**  
```{r, echo=FALSE}
library(knitr)
```


## **1. Loading Data**
We load the dataset
```{r}
data(mtcars)
head(mtcars)
```

Motor Trend Car Road Tests

_Description_ 

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).

_Format_

A data frame with 32 observations on 11 (numeric) variables.

|      |     |       | 
|------|-----|-------|
|[, 1]| mpg	 |Miles/(US) gallon|
|[, 2]|	 cyl|	 Number of cylinders|
|[, 3]|	 disp|	 Displacement (cu.in.)|
|[, 4]|	 hp	 |Gross horsepower|
|[, 5]|	 drat|	 Rear axle ratio|
|[, 6]|	 wt	 |Weight (1000 lbs)|
|[, 7]|	 qsec|	 1/4 mile time|
|[, 8]|	 vs	 |Engine (0 = V-shaped, 1 = straight)|
|[, 9]|	 am	 |Transmission (0 = automatic, 1 = manual)|
|[,10]|	 gear|	 Number of forward gears|
|[,11]|	 carb|	 Number of carburetors|

```{r, echo=FALSE}
## loading libraries
library(car) 
library(GGally)
library(ggplot2)
```

For convenience we can convert the variable "am" to a factor and add a more clear classification "Automatic" & "Manual".  and we can perform a friefly analysis of both variables
```{r}
mtcars$am = as.factor(mtcars$am)
levels(mtcars$am) = c("Automatic", "Manual")
summary(mtcars$mpg); summary(mtcars$am)
```
# **2.EDA**
```{r}
scatterplotMatrix(~mpg+disp+drat+wt+hp|am, data=mtcars, col = c("skyblue4", "indianred4"), main="Type of Transmission", cex.labels= 1,cex.main=2, cex=1.5)
```

```{r}
boxplot(mpg~am,data = mtcars,xlab = "Transmission Automatic,Manual", ylab = "MPG", main="MPG by Transmission Type", col=c("skyblue4", "indianred4"))
```
#**3. t-test**
```{r}
hist(mtcars$mpg, breaks=10, xlab="MPG", main="MPG histogram", col = "skyblue3")

```
```{r}
plot(density(mtcars$mpg), main="kernel density", xlab="MPG", col="lightpink4" )
```


```{r}
library(GGally)
library(ggplot2)    

gp = ggpairs(mtcars, lower = list(continuous = "smooth"))
gp
```
Interpretation : In this plot, we see many multi-collinearity, and it suggests that we should NOT use all the variables as predictor otherwise it will be overfitting.

# **4.Quantify the MPG difference between automatic and manual transmissions**

Consider all the other varaibles as possible predictor and MPG as outcome. Use R step function to find out the best fit model

First, Glimpse at all relationship between each variable

**Finding best model**
```{r}
best_model<-step(lm(mpg ~ .,data = mtcars), trace=0)
summary(best_model)
```

```{r}
#par(mfrow=c(2,2))
plot(best_model)
```
We can conclude that the best model are with wt/qsec/am as predictor and the R-square is 84.97%, which is good fitting to mpg outcome.The mpg of manual cars is 2.9358 mpg better than that of automatic cars. 
