---
title: "Shiny Application and Reproducible Pitch Presentation"
author: "Gabriela Ochoa"
date: "29 marzo 2021"
output: ioslides_presentation
---
# Looking for a car that fits **you** perfectly?

## Introduction

This presentation is done as part of the final course project for `Developing Data Products` course in the Data Science Specialization track by *John Hopkins University on Coursera*.

## The Application 

With this application you'll find different options which will help you choose a car that fits your own needs.

You may enter `distance`, `price of gas`, etc, and the app will display different cars options.

Additionally, you can also choose some characteristics of the cars that you desire: `Cylinders`, `Displacement`, `Horse Power` and `Transmission`. 

## Dataset Overview

The application uses 'mtcars' dataset from the 'datasets' package in R which lists down 10 aspects of automobile design and performance for 32 cars.

```{r, echo=TRUE, comment=""}
library(datasets)
data(mtcars)
head(mtcars, 4)

```

## Variable Correlation

```{r, echo=TRUE, comment=""}
library(datasets)
data(mtcars)
cor(mtcars)

```